Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
* Quelque chose ne va pas avec cette phrase.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@119 403e655e-980a-47bd-8c60-1ee5348bb6b7

We propose to discuss a small part of these questions, namely the
enhancement and adaptation of version control paradigms to the
management of mathematical repositories, to witness with more
precision the \emph{impact of changes}. Following the Type Theory
approach, our work is based on an algebra of expressive types that are
meant to assign precise specifications to object-level term
constructors and, in the meantime, to capture fine-grained
dependencies between these objects.

>>>>

We propose to discuss a small part of these questions, namely the
enhancement and adaptation of version control paradigms to the
management of mathematical repositories, to witness with more
precision the \emph{impact of changes}. Following the Type Theory
approach, our work is based on an algebra of expressive types that are
meant to assign precise specifications to object-level term
constructors and, in the meantime, capture fine-grained
dependencies between these objects.
